Stylistic Context Clustering for Token-Level Author Diarization

### 2017-09-01 paper/paper.tex
Merged 2 paragraphs
Improved some text

Our approach can generally be described as a pipeline of three transformations: basic feature extraction $f_\mathrm{b}$, feature transformation $f_\mathrm{t}$ and clustering $f_\mathrm{c}$.

The basic feature extractor denoted with $f_\mathrm{b}$ is used to extract stylistic features from the contexts of all tokens. If $D$ is a document with $n$ tokens, the basic feature extractor outputs a sequence of $n$ $n_\mathrm{b}$-dimensional feature vectors representing the contexts of tokens. The next step in the pipeline is the feature transformation $f_\mathrm{t}$ that maps the basic features to a $n_\mathrm{t}$-dimensional space that they can be better clustered in. The final step in the pipeline is clustering denoted with $f_\mathrm{c}$. The clustering algorithm implicitly clusters tokens because it actually clusters their stylistic contexts, each cluster representing an author. Depending on the task, the clustering algorithm can either be given a known number of authors, or try to predict it.

@@

For both Models A and B we calculated standard errors and wanted to obtain $95\%$ t-based confidence intervals. Since the test sets are small, D’Agostino and Pearson’s normality test at $p=0.05$ was performed first. The Model A data in all tasks did not provide enough evidence to reject the null hypothesis that a sample comes from a normal distribution. In test of Model B's both $F_1$-scores, the data provided enough evidence to reject the null hypothesis.

Although the Model A achieved the highest micro and macro-averaged $F_1$-scores on the Task \emph{a}, this task seemed to be very difficult. $F_1$-scores of Model A are only slightly above the Single-author dummy baseline and lower $95\%$ limit for macro-$F_1$ is $0.15$. Model A also achieved the best, but actually not very good performance on the Task \emph{b} with $(0.57, 0.67)$ $95\%$ confidence interval. Although Model B behaved reasonably well on the Task \emph{c}, a better way of estimating a true number of clusters is needed.

>>>>

Our approach can generally be described as a pipeline of three transformations: basic feature extraction $f_\mathrm{b}$, feature transformation $f_\mathrm{t}$ and clustering $f_\mathrm{c}$. The basic feature extractor denoted with $f_\mathrm{b}$ is used to extract stylistic features from the contexts of all tokens. If $D$ is a document with $n$ tokens, the basic feature extractor outputs a sequence of $n$ $n_\mathrm{b}$-dimensional feature vectors representing the contexts of tokens. The next step in the pipeline is the feature transformation $f_\mathrm{t}$ that maps the basic features to a $n_\mathrm{t}$-dimensional space that they can be better clustered in. The final step in the pipeline is clustering denoted with $f_\mathrm{c}$. The clustering algorithm implicitly clusters tokens because it actually clusters their stylistic contexts, each cluster representing an author. Depending on the task, the clustering algorithm can either be given a known number of authors, or try to predict it.

@@

For both Models A and B we calculated standard errors and wanted to obtain $95\%$ t-based confidence intervals. Since the test sets are small, D’Agostino and Pearson’s normality test with p-value $0.05$ was performed first. The Model A data in all tasks did not provide enough evidence to reject the null hypothesis that a sample comes from a normal distribution. In test of Model B's both $F_1$-scores, the data provided enough evidence to reject the null hypothesis.

Although the Model A achieved the highest micro and macro-averaged $F_1$-scores on the Task \emph{a}, this task seemed to be very difficult. $F_1$-scores of Model A are only slightly above the Single-author dummy baseline and lower $95\%$ limit for macro-$F_1$ is $0.15$. Model A also achieved the best, but actually not very good performance on the Task \emph{b} with $(0.57, 0.67)$ $95\%$ confidence interval. Although Model B behaved reasonably well on the Task \emph{c}, a better way of estimating the number of clusters is needed.
